# MT is Better than AT for Fuel Efficiency
### By Marco Xu
## Exclusive Summary and Synopsis
This report tries to answer these two questions.
##### ¡°Is an automatic or manual transmission better for MPG¡± & 
##### ¡°Quantify the MPG difference between automatic and manual transmissions¡±
##### I take the mtcars data set and write up an analysis to answer their question using regression models and exploratory data analyses.

## Part1 "Is an automatic or manual transmission better for MPG¡±
We may take a glimpse of the mtcars data. First use the cor function to get the correlations between mpg and each of other variables. Also we will draw a plot Figure 1 of correlations between different variables with "corrplot.mixed".
```{r}
library(datasets)
library(corrplot)
summary(mtcars)
```

Second we will draw the box plot Figure 2 of the mpg variable against the influence by factor am with "boxplot"

## Part2 Quantify the MPG difference between automatic and manual transmissions
First, we try to find some relations
```{r}
bartlett.test(mpg ~ am, data = mtcars)$p.value
```
The p-value is significantly small, thus we will draw to the conclusion that the variable am influences the mean of different cars¡¯ MPG.
```{r,results='hide'}
fit.whole <- lm(mpg ~ ., data = mtcars)
fit.optimal <- step(fit.whole, direction = 'both')
```
```{r}
summary(fit.optimal)
```
Then we plot them with "plot".

This is the end of the main text
#### _______________________________________________________________________________________________________________________________


## Appendix
#### Part1 Figure1
```{r}
M <- cor(mtcars)
corrplot.mixed(M, lower = "number", upper = "circle", title= "Correlations between Different Variances")
```
#### Part1 Figure2
```{r}
boxplot(mpg ~ am, data = mtcars, col=c("steelblue","hotpink"),names = c("Automatic", "Manual"),las=1, font.lab=2)
```
#### Part2 Figure
```{r}
par(mfrow = c(2,2))
plot(fit.optimal)
```

This is the end of the appendix 